\documentclass[a4paper,20pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}
\usepackage{hyperref}
\hypersetup{
  colorlinks=true,   
  urlcolor=blue,
}
\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.530in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.45in}
\addtolength{\textheight}{1in}

\urlstyle{rm}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-10pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-6pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeItemWithoutTitle}[1]{
  \item\small{
    {\vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{#3} & \textit{#4} \\
    \end{tabular*}\vspace{-5pt}
}


\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-3pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-----------------------------
%%%%%%  CV STARTS HERE  %%%%%%

\begin{document}

%----------HEADING-----------------
\begin{center}
    \textbf{\Huge \scshape Dipankar Das} \\ \vspace{2pt}
    \href{mailto:dipankar@dipankar-das.com}{dipankar@dipankar-das.com} \quad \Large\textbar \quad
    +91-9546515939 \quad \Large\textbar \quad
    \href{https://dipankar-das.com/}{dipankar-das.com} \quad \Large\textbar \quad
    \href{https://www.linkedin.com/in/dipankar-das-1324b6206/}{LinkedIn} \quad \Large\textbar \quad
    \href{https://github.com/dipankardas011}{GitHub}
\end{center}


%-----------PROFESSIONAL SUMMARY-----------------
\section{Professional Summary}
\vspace{5pt}
\small{Systems-focused DevOps Engineer with 2+ years of experience specializing in cloud-native architecture, infrastructure modernization, and high-concurrency distributed systems. Architected multi-cloud orchestration engines in \textbf{Go} and led zero-downtime migrations for \textbf{Fortune 500} and \textbf{FinTech} enterprises. Proven track record in optimizing cloud spend by \textbf{20\%} via advanced FinOps strategies and enhancing reliability through \textbf{OpenTelemetry}. Founder of the \textbf{ksctl} ecosystem, dedicated to building developer-centric efficiency tools and scalable multi-cloud infrastructure.}
\vspace{5pt}


%-----------SKILLS-----------------
\section{Skills Summary}
	\resumeSubHeadingListStart
        \resumeSubItem{Languages}{~~~~~~Go, C, Python, Rust, Java, JavaScript, C++}
        \resumeSubItem{Tools}{~~~~~~~~~~~~~~Kubernetes, Docker, MongoDB, MariaDB, NATS, Redis, Jenkins, Ansible, Terraform, Vault}
        \resumeSubItem{Concepts}{~~~~~~~~Event-driven systems, CQRS, DDD, Event Sourcing (familiar)}
        \resumeSubItem{Platforms}{~~~~~~~AWS, Azure, Hetzner, GCP, Linux}
        \resumeSubItem{Soft Skills}{~~~~~~~Project Maintainer, Planing, Tech. Writing, Time Management and Automating things}
    \resumeSubHeadingListEnd
\vspace{-5pt}


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading{rtCamp}{Pune, India}
    {DevOps Engineer}{Jan 2024 - Present}
  \resumeItemListStart
        \resumeItem{Enterprise IaC \& Migration (Cox Automotive)}
          {Spearheaded a zero-downtime migration of legacy AWS infrastructure into \textbf{Terraform}. Remediated critical gaps by importing manually managed \textbf{CloudFront} distributions, \textbf{S3} assets, and \textbf{WAF} policies into a standardized multi-environment GitOps workflow, ensuring 100\% configuration consistency and eliminating "Click-ops". Established a rigorous \textbf{Plan-Review-Apply} SOP for infrastructure changes, ensuring zero configuration drift across multi-cloud production environments.}
        
        \resumeItem{Cloud-Native Scaling \& Observability}
          {Architected the migration of a monolithic \textbf{Frappe/ERPNext} platform to a distributed \textbf{Kubernetes} cluster for a global FinTech platform. Decoupled core services to handle high-concurrency traffic and implemented \textbf{OpenTelemetry (OTel)} for full-stack instrumentation (logs, traces, metrics), reducing MTTR by providing deep visibility into distributed worker bottlenecks.}
        
        \resumeItem{Cloud FinOps \& Cost Engineering}
          {Achieved a \textbf{20\% reduction in cloud OpEx} by optimizing Kubernetes compute strategies. Engineered specialized Node Groups utilizing \textbf{Spot Instances} and implemented \textbf{scale-to-zero logic} for memory-intensive background tasks and cron jobs, ensuring high performance while minimizing idle resource waste.}

        \resumeItem{Product Engineering (EasyDash / EasyEngine)}
          {Co-developed a high-scale \textbf{Cloud Provisioning Engine} for \textbf{dash.easyengine.io} using \textbf{Python, Terraform, and Ansible}. Engineered the automated backend for rapid WordPress/PHP deployments, facilitating a successful market launch that generated \$200+ in initial subscription revenue within 60 days.}

        \resumeItem{Automation \& Developer Experience}
          {Optimized \textbf{GitHub Self-Hosted Runners} with resource-aware labeling and multi-container environments, drastically reducing CI/CD wait times. }
      \resumeItemListEnd

  \vspace{2pt}

  % \resumeSubheading{kubmin -- ksctl}{Remote}
  % {Founder \& Principal Engineer}{Jun 2025 -- Present}
  % \resumeItemListStart
  %   \resumeItem{System Design}{Architected Go-based stateless service which can share horizontally which is bascked by SQLite (Turso), Redis caching, Rate Limiting, and NATS messaging for event based system, thus enabling cluster's workload lifecycle management across AWS, Azure, and GCP.}
  %   \resumeItem{Asynchronous Task Processing}{Built event-driven worker system with NATS messaging for long-running cluster operations, improving API responsiveness and enabling horizontal scalability. In Process got to create custom Statemachine for handling complex workflows from retry logic to what all errors can be retried with exploiting NAK and ACK mechanism.}
  %   \resumeItem{Enterprise RBAC \& Quota System}{Implemented role-based access control with Authzed and multi-tenant quota enforcement for workload management across organization hierarchies.}
  %   \resumeItem{Full-Stack Platform}{Developed Next.js (App Router) SaaS frontend with TypeScript, Tailwind CSS, and shadcn/ui, featuring real-time monitoring and developer-centric UI.}
  %   \resumeItem{Agentic Workflows}{Leveraging Claude Code and Gemini CLI models to build autonomous agents during development phase of this paltform to help developers with higher velocity and less cognitive load.}
  %   \resumeItem{Website}{\href{https://ksctl.com/product/kubmin/}{Link to Detailed view}}
  % \resumeItemListEnd
\resumeSubheading{kubmin -- ksctl}{Remote}
  {Founder \& Principal Engineer}{Jun 2025 -- Present}
  \resumeItemListStart
    \resumeItem{Distributed Orchestration Engine}
      {Architected a cloud-agnostic provisioning engine in \textbf{Go} to manage Kubernetes lifecycles across AWS, Azure. Engineered a high-availability state layer using \textbf{Turso (Edge SQLite)} and \textbf{Redis}, enabling idempotent cluster operations with a minimal infrastructure footprint.}
    
    \resumeItem{Pragmatic Task Orchestration}
      {Developed a lightweight, event-driven \textbf{state machine} using \textbf{NATS JetStream}. Optimized for operational simplicity over heavy frameworks like Temporal, implementing custom NAK/ACK and retry logic to ensure 100\% reliability during long-running infrastructure tasks.}
    
    \resumeItem{Scalable Access Governance (ReBAC)}
      {Implemented a \textbf{Relationship-Based Access Control} system using \textbf{Authzed (SpiceDB)}. Designed a hierarchical sharing model (Org, Cluster, Workload) to handle complex multi-tenant permissions and quota enforcement across distributed engineering teams.}

    \resumeItem{Developer Efficiency Analytics}
      {Designed an engine to track \textbf{container image behavior across versions}, providing developers with data-driven insights into performance and energy regressions. Enabled teams to baseline and optimize software efficiency within the Kubernetes deployment pipeline.}
    
    \resumeItem{AI-Augmented Engineering}
      {Integrated \textbf{Claude Code and Gemini CLI} into the platform development workflow. Leveraged AI-agentic patterns to accelerate platform delivery by 40\% while maintaining high code quality and consistency.}
    \resumeItem{Website}{\href{https://ksctl.com/product/kubmin/}{Link to Detailed view}}
  \resumeItemListEnd

  \vspace{2pt}
    \resumeSubheading{Viamagus}{Remote}
    {DevMLSecOps Consultant POC (Freelance)}{Feb 2025 -- Apr 2025}
    \resumeItemListStart
      \resumeItem{Integrating vulnerabilities finder inside their CI}{used OWASP ZAP to help the team find bugs in their APIs like SQL injection, man-in-middle attacks for their web applications and APIs}
      \resumeItem{Integrating Snyk into their Code Review Pipeline}{into their CI pipelines for vulnerability scanning.}
      \resumeItem{Optimized internal LLM-based projects}{Helped containerization and even created resport on what are the real benchmarks interms of image size, network/disk performance.}
      \resumeItem{Deploying OSS LLM Models}{Deployed vLLM and ollama with AWS Auto Scaling Groups and VPC PrivateLink infrastructure.}
    \resumeItemListEnd

\vspace{2pt}
    \resumeSubheading
		{Open Source Contributions}{Remote}
		{Self-Employed (Part-time) worked on Rust, Go, JavaScript, CI/CD Pipelines, Documentation}{Feb 2022 -  Present}
		\resumeItemListStart
        \resumeItem{For Detailed view}{\href{https://dipankar-das.com/posts/projects/\#my-open-source-contributions}{Link to Detailed view}}
		\resumeItemListEnd

\vspace{2pt}
\resumeSubHeadingListEnd

%-----------PROJECTS-----------------
\vspace{-5pt}
\section{Projects \href{https://dipankar-das.com/posts/projects/\#my-project-collection}{Detailed view}}
\resumeSubHeadingListStart

\resumeSubheading{KsctlCli - \href{https://ksctl.com/product/ksctlcli/}{Github Link}}{Cloud Agnostic Kubernetes management tool}
    {Founder \& Lead Developer}{Sep 2022 - Sep 2025}
    \begin{description}[font=$\bullet$]
        \item {A Generic Kubernetes Management CLI tool for various cloud providers}
        \item {Worked with NATS and event-driven patterns in internal tools.}
        \item {Integrated with MongoDB, SQLite (Turso), Docker, and Kubernetes APIs.}
        \item {Tech: Go, Kubernetes, AWS, Azure, Civo, GCP, Docker, Cosign, System Design}
    \end{description}

\resumeSubheading{WAE - WASI App Experiment - {\href{https://dipankar-das.com/posts/projects/#wae-wasi-app-experiment}{Link}}}{AI and WASM}
    {Creator and Maintainer, Wattime, OpenAI, WASM}{Jul 2024 - Aug 2024}
    \begin{description}[font=$\bullet$]
        \item {Built a modular WebAssembly (WASI) app using multiple language runtimes for end-to-end automation.}
        \item {Demonstrated multi-service orchestration with persistent local storage and cross-component comms.}
        \item {was able to achieve multi language code base on single build system by using WASI@v2}
        \item {Tech: Rust, WASM, Python, OpenAI, WattTime, GitHub API}
    \end{description}

\resumeSubheading{Chat bot - {\href{https://dipankar-das.com/posts/projects/\#chat-bot-using-gpt-2}{Link}}}{LLM and WASM}
    {Creator \& Maintainer, Transformer, WASM}{Jun 2023 - Jul 2023}
    \begin{description}[font=$\bullet$]
        \item {Create HTTP server using rust as a wasm module and have it to handle request for the text2text generator machine learning model running on huggingface}
        \item {Tech: Rust, WASM, Python, FastAPI, HuggingFace}
    \end{description}

\resumeSubHeadingListEnd

%-----------Certificates-----------------
\vspace{-5pt}

\section{Certificates}
\begin{description}[font=$\bullet$]
\item {All certificates and badges \href{https://dipankar-das.com/posts/aboutme/#certificates-and-badges}{certificates}}

\end{description}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {KIIT University}{Bhubaneswar, India}
      {Bachelor of Technology in Computer Science; GPA: 9.17}{Aug 2020 - Jun 2024}
  \resumeSubHeadingListEnd

%-----------LANGUAGES-----------------
\vspace{-5pt}

\section{Languages}
\begin{description}[font=$\bullet$]
\item {English - Native or bilingual proficiency}

\end{description}

%-----------VOLUNTEER-----------------
\vspace{-5pt}
\section{Volunteer Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
    {CNCF Green Reviews (Contributor)}{Global}
    {Aim to measure carbon footprint of CNCF projects}{}
    \begin{itemize}[leftmargin=*]
        \item Reviewed CNCF projects for sustainability and environmental impact.
        \item Worked on SCI scoring and Golang monitoring tooling.
    \end{itemize}
    \resumeSubheading
    {Kubesimplify (Ambassador)}{Global}
    {Simplify Cloud native concepts | created and maintained a project, tech. blogs}{}

\resumeSubHeadingListEnd

\end{document}

